\section{README for Glibc optimization project}
\label{group__project__readme}\index{README for Glibc optimization project@{README for Glibc optimization project}}
the glibc candidate (test) function directories

Doxygen documentation is avaiable for the project. Use either

doxygen -g doxygen.config

or

make doc

to generate.

Common Elements

Each directory below constitutes a performance and unit test suite for evaluating and optimizing a given glibc func. The functions from the various sysdeps subdirectories are copied here, minimally edited (e.g. renaming the function to $<$arch$>$\_\-$<$func$>$), and link with the utest and ptest applications.

$\backslash$subsection define\_\-ptest ptest

ptest is the peformance test, and is uses the framework in common for standard options handling, test inner and outer loops, statitistics gathering and reporting.

$\backslash$subsection define\_\-utest utest

the unit test application for each candidate. Typically these use oversized buffers to check for overruns and underruns.

$\backslash$subsection reference\_\-imp Reference Implementation memset contains the \char`\"{}canonical form\char`\"{} of ptest, which can be branched and modified for any additional candidates.

Creating a new test

$\backslash$subsection test\_\-must Things you will need to modify:

{\bf {\bf T\_\-def\_\-Fn}}

this needs to be defined to match the prototype of the function under test

{\bf {\bf def\_\-tests}[$\,$]}

needs to contain the function pointer and name of the implementations to test

{\bf DO\_\-TEST\_\-NEXT}

needs to contain the instructions to move through the buffers

{\bf DO\_\-TEST\_\-RUN}

needs to have the invocation line for the function under test (Note: the variables to use must be visible inside the do\_\-test\_\-func boilerplate)

{\bf Makefile}

LGPL\_\-OBJS, BSD\_\-OBJS to include the functions under test

$\backslash$subsection test\_\-may Things you may need to modify

{\bf Options}

you can add options easily calling the opts\_\-def function with useful automated value setting (c.f. \char`\"{}Standard Actions\char`\"{} in common/include/opts\_\-util.h). Add these just below test\_\-init in ptest.c:main.

{\bf {\bf main()}} while ... opts\_\-getopt (in ptest.c)

you may need some behavior not easily supported in the T\_\-opts\_\-action callback

{\bf {\bf T\_\-test\_\-buffer::f\_\-wrap}}

You may need to override this if you need to refill the src or dst buffer on wrap-around.

{\bf {\bf T\_\-test\_\-buffer::f\_\-count}}

if the buffer contents need to change for each count (for example strlen) you can set f\_\-count to a new count change operation. Please examine the default implementation for semantices. 